\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-20 doc/incertae_sedis.tex
consolidating similar points

Ideally, the \emph{incertae sedis}
annotation some taxon $x$ would be accompanied by a specific
statement about which other taxa might include $x$.
Detailed
readings of the character argumentation used by taxonomists could
provide this sort of specific information in many cases, but we lack
such information on the scale of the entire OTT.
Here we consider a
few operational approaches for handling the \emph{incertae sedis}
label.

@@

In principle this information is easy to incorporate.
If
$\mathcal{P}$ is the set of taxa that are potential ancestors for
incertae sedis taxon $x$, then $\mathcal{L}(x)$ will occur in neither
the include nor the exclude set of any taxon in $\mathcal{P}$.
Unfortunately, utilizing taxon-specific interpretations of the
incertae sedis flag relies on character argumentation (which is
lacking in OTT) or rank-based information (which is frequently
untrustworthy in OTT).
Thus, here we pursue an approach of ascribing a
meaning to the \emph{incertae sedis} label which attempts to capture
the core of the idea that it articulates, but which can be applied
automatically across the taxonomy without additional information.

>>>>

@@

In principle this information is easy to incorporate.
Ideally, the \emph{incertae sedis}
annotation some taxon $x$ would be accompanied by a specific
statement about which other taxa might include $x$.
If $\mathcal{P}$ is the set of taxa that are potential ancestors for
incertae sedis taxon $x$, then $\mathcal{L}(x)$ will occur in neither
the include nor the exclude set of any taxon in $\mathcal{P}$.
Unfortunately, utilizing taxon-specific interpretations of the
incertae sedis flag relies on detailed readings of character argumentation
(which is lacking in OTT) or rank-based information (which is frequently
untrustworthy in OTT).
Thus, here we pursue an approach of ascribing a
meaning to the \emph{incertae sedis} label which attempts to capture
the core of the idea that it articulates, but which can be applied
automatically across the taxonomy without additional information.
